Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2019-09-09 GWLDCII.tex
adjusted the locally same remark

With this setup, if we can find a vertex $\ell$ occurring after both $i$ and $m$ such that the \emph{configuration} of propagators ending in the interval $[j-1, \ell+1]$ is identical in both $W'$ and $V'$, then the vertices contributed to $I_i^W$ and $I_m^V$ are the same from step $j$ to step $\ell$ (inclusive). See Figure~\ref{fig:locally identical} for an illustration of this.

>>>>

With this setup, if we can find a vertex $\ell$ occurring after both $i$ and $m$ such that the \emph{configuration}\note{Why is configuration italicized?} of propagators ending in the interval $[j-1, \ell+1]$ is identical in both $W'$ and $V'$, then the vertices contributed to $I_i^W$ and $I_m^V$ are the same from step $j$ to step $\ell$ (inclusive). See Figure~\ref{fig:locally identical} for an illustration of this.

Furthermore, if the propagators of $W'$ and $V'$ ending in the interval $[j-1, \ell+1]$ are also identically labelled, then $I_i^W$ and $I_m^V$ are the same as functions when restricted to those propagators.
